Mechanistic Bayesian Forecasts of COVID19

### 2020-07-29 paper.tex
update

\begin{figure}
  \centering
     \begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.3]{US.png}
    \caption{US}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.3]{NY.png}
    \caption{New York}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.3]{FL.png}
    \caption{Florida}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.3]{CA.png}
    \caption{California}
\end{subfigure}%

\caption{Example fit and forecast for four states.}
\label{fig:fit_and_forecast_results}
\end{figure}

@@

@@

@@

>>>>

\begin{figure}
  \centering

    \includegraphics[scale=.2]{fit_and_forecast_results.png}

\caption{Example fit and forecast for states with over 50 incident deaths.}
\label{fig:fit_and_forecast_results}
\end{figure}

@@

\item \textbf{MechBayes is biased high}. We can see from Figure \ref{fig:bias} that MechBayes was biased high with respect to the median forecast. We suspect this is due to the inherent exponential growth of an SEIR model when the number of susceptibles is small. Since overall prevalence in any state is well below the number needed to reach herd immunity, when the model sees an increase in cases it treats this as exponential growth, which translates into exponential growth in deaths. However, in the recent forecasts the bias is consistently lower than the COVID-HUB baseline model. Note the extreme low bias in the first submission is due to the omission of the U.S. in the submission. \textbf{is this true} \textbf{something is telling me this is also related to the exponential random walk}

\item \textbf{MechBayes is probabilistically well-calibrated compared with the baseline model}. Small WIS values are better in terms of calibration \cite{bracher2020evaluating}. The two sources of uncertainty in MechBayes come from the distribution over the differential equation parameters and the observation noise, unlike a fully stochastic model that has inherent variability within the differential equation transitions. This suggest that even a deterministic model core can produce well calibrated prediction intervals by capturing the uncertainty in parameter estimation and observation noise.

@@

\begin{figure}
\includegraphics[scale=.2]{bias_by_timezero.png}

\caption{Bias of MechBayes and COVID-Baseline as a function of time. }
\label{fig:bias}
\end{figure}

@@

However, using relatively simple non-parametric methods we were able to beat the COVID-HUB baseline model in both point and probabilistic forecast evaluations. Our nested model comparisons show that extending the basic SEIR compartmental to real-world pandemic challenges improves forecasting accuracy.
